Models pretest

### 2022-12-08 Submission/Models_pretest.Rmd
Updated models

adr <- data.frame(year = c(1985, 1986, 1987), def_year = c(21.050, 21.050, 21.050))
# Missing year data
amazon_def_year <- rbind(adr, amazon_def_year) 

@@

@@

@@

```{r models, fig.cap="Logistic Regressions", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE, results="asis"}

ama_model <- dplyr::left_join(ama_mx, amazon_def_year, by = "year") %>%
dplyr::left_join(AAI, by = "year") %>%
filter(location_cat != "Non Identified", mx_cat != "Other Mixed-types") %>%
  mutate(con_vs_all = ifelse(mx_cat == "Pure Environmental Conservation", 1, 0),
         EI_vs_all = ifelse(mx_cat == "Pure Economic Integration", 1, 0),
         SD_vs_all = ifelse(mx_cat == "Pure Social Development", 1, 0),
         sov_vs_all = ifelse(mx_cat == "Pure National Sovereignty", 1, 0))

ama_model2 <- dplyr::select(pop, -text) %>%
  dplyr::left_join(amazon_def_year, by = "year") %>%
  dplyr::left_join(AAI, by = "year") %>%
  filter(location_cat != "Non Identified") %>%
  mutate(location_cat = ifelse(grepl("parana|paraiba|mato grosso|mato grosso do sul", location, ignore.case = TRUE), "Non Amazonian States", location_cat),
         location_cat = ifelse(grepl("paraguay", location, ignore.case = TRUE),
                               "International", location_cat),
         location_cat = factor(ifelse(grepl("Bolivia|Peru|Ecuador|Colombia|Venezuela|Guyana|Suriname",
                                            location), "Amazonian Countries",
                                      location_cat),
                               levels = c("Amazonian States",
                                          "Amazonian Countries",
                                          "International", "Brasilia",
                                          "Non Amazonian States")),
         election_year = ifelse(grepl("1989|1994|1998|2002|2006|2010|2014|2018",
                                      year), 1, 0))

# model
a1 <- glm(con_vs_all ~ as.factor(location_cat) + election_year +
                         def_year + AAI + party, family=binomial(link = "logit"),
                       data = ama_model)
a2 <- glm(EI_vs_all ~ as.factor(location_cat) + election_year +
                        def_year + AAI + party, family=binomial(link = "logit"),
                      data = ama_model)
a3 <- glm(SD_vs_all ~ as.factor(location_cat) + election_year +
                        def_year + AAI + party,
                      family=binomial(link = "logit"), data = ama_model)
a4 <- glm(sov_vs_all ~ as.factor(location_cat) + election_year +
                         def_year + AAI + party,
                       family=binomial(link = "logit"), data = ama_model)
a5 <- glm(amazon_speech ~ as.factor(location_cat) + election_year +
                         def_year + AAI + party,
                       family=binomial(link = "logit"), data = ama_model2)

stargazer::stargazer(a1, a2, a3,
                     a4, a5, digits = 6,
                     no.space = TRUE, title = "Logistic Regressions")
```

@@

```{r models fe, fig.cap="Fixed-effects Regressions", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE, results="asis"}

# model fe
b1 <- plm(con_vs_all ~ as.factor(location_cat) + election_year +
                         def_year + AAI + party, data = ama_model,
                         model = "within", index = "year")
b2 <- plm(EI_vs_all ~ as.factor(location_cat) + election_year +
                         def_year + AAI + party, data = ama_model,
                         model = "within", index = "year")
b3 <- plm(SD_vs_all ~ as.factor(location_cat) + election_year +
                         def_year + AAI + party, data = ama_model,
                         model = "within", index = "year")
b4 <- plm(sov_vs_all ~ as.factor(location_cat) + election_year +
                         def_year + AAI + party, data = ama_model,
                         model = "within", index = "year")
b5 <- plm(amazon_speech ~ as.factor(location_cat) + election_year +
                         def_year + AAI + party, data = ama_model2,
                         model = "within", index = "year")

stargazer::stargazer(b1, b2, b3,
                     b4, b5, digits = 6,
                     no.space = TRUE, title = "Fixed-effects Regressions")
```

@@

```{r models lagged, fig.cap="Logistic Regressions Output Lagged Deforestation", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE, results="asis"}

amazon_def_year <- readRDS("~/Documents/GitHub/amazondef/Replication_files//amazon_def_year.Rds")
amazon_def_year$year <- amazon_def_year$year + 1
adr <- data.frame(year = c(1985, 1986, 1987, 1988),
def_year = c(21.050, 21.050, 21.050, 21.050))
# Missing year data
amazon_def_year <- rbind(adr, amazon_def_year)

ama_model2_lag <- dplyr::select(pop, -text) %>%
  dplyr::left_join(amazon_def_year, by = "year") %>%
  dplyr::left_join(AAI, by = "year") %>%
  filter(location_cat != "Non Identified") %>%
  dplyr::mutate(location_cat = ifelse(grepl("parana|paraiba|mato grosso|mato grosso do sul", location, ignore.case = TRUE), "Non Amazonian States", location_cat),
         location_cat = ifelse(grepl("paraguay", location, ignore.case = TRUE),
                               "International", location_cat),
         location_cat = factor(ifelse(grepl("Bolivia|Peru|Ecuador|Colombia|Venezuela|Guyana|Suriname",
                                            location), "Amazonian Countries",
                                      location_cat),
                               levels = c("Amazonian States",
                                          "Amazonian Countries",
                                          "International", "Brasilia",
                                          "Non Amazonian States")),
         election_year = ifelse(grepl("1989|1994|1998|2002|2006|2010|2014|2018",
                                      year), 1, 0))

# model
c1 <- glm(con_vs_all ~ as.factor(location_cat) + election_year +
                         def_year + AAI + party, family=binomial(link = "logit"),
                       data = ama_model_lag)
c2 <- glm(EI_vs_all ~ as.factor(location_cat) + election_year +
                        def_year + AAI + party, family=binomial(link = "logit"),
                      data = ama_model_lag)
c3 <- glm(SD_vs_all ~ as.factor(location_cat) + election_year +
                        def_year + AAI + party,
                      family=binomial(link = "logit"), data = ama_model_lag)
c4 <- glm(sov_vs_all ~ as.factor(location_cat) + election_year +
                         def_year + AAI + party,
                       family=binomial(link = "logit"), data = ama_model_lag)
c5 <- glm(amazon_speech ~ as.factor(location_cat) + election_year +
                         def_year + AAI + party,
                       family=binomial(link = "logit"), data = ama_model2_lag)

stargazer::stargazer(c1, c2, c3,
                     c4, c5, digits = 6,
                     no.space = TRUE, title = "Logistic Regressions with Lagged Year")
```

@@

```{r models lagged ideology, fig.cap="Logistic Regressions Output Lagged Deforestation with Ideology", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE, results="asis"}

#table(ama_model$president, ama_model$party)

ideology_vdem <- readRDS("~/Documents/GitHub/amazondef/Submission/V-Dem-CPD-Party-V2.rds") %>% 
dplyr::filter(country_name == "Brazil") %>%
dplyr::select(v2pashname, v2xpa_antiplural, v2xpa_popul, v2pariglef) %>%
tidyr::drop_na() %>%
dplyr::rename(party = v2pashname) %>%
group_by(party) %>%
summarise(anti_pluralism = mean(v2xpa_antiplural),
populism = mean(v2xpa_popul),
left_right = mean(v2pariglef))

ama_model_lag <- dplyr::left_join(ama_model_lag, ideology_vdem)

ama_model2_lag <- dplyr::left_join(ama_model2_lag, ideology_vdem)

# model
c1 <- glm(con_vs_all ~ as.factor(location_cat) + election_year +
                         def_year + AAI + populism + anti_pluralism + left_right, family=binomial(link = "logit"),
                       data = ama_model_lag)
c2 <- glm(EI_vs_all ~ as.factor(location_cat) + election_year +
                        def_year + AAI + populism + anti_pluralism + left_right, family=binomial(link = "logit"),
                      data = ama_model_lag)
c3 <- glm(SD_vs_all ~ as.factor(location_cat) + election_year +
                        def_year + AAI + populism + anti_pluralism + left_right,
                      family=binomial(link = "logit"), data = ama_model_lag)
c4 <- glm(sov_vs_all ~ as.factor(location_cat) + election_year +
                         def_year + AAI + populism + anti_pluralism + left_right,
                       family=binomial(link = "logit"), data = ama_model_lag)
c5 <- glm(amazon_speech ~ as.factor(location_cat) + election_year +
                         def_year + AAI + populism + anti_pluralism + left_right,
                       family=binomial(link = "logit"), data = ama_model2_lag)

stargazer::stargazer(c1, c2, c3,
                     c4, c5, digits = 6,
                     no.space = TRUE,
                     title = "Logistic Regressions with Lagged Year and Party Ideology")
```

```{r models president fixed effect, fig.cap="Logistic Regressions Output with President fixed effecr", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE, results="asis"}

d1 <- plm(con_vs_all ~ as.factor(location_cat) + 
                         def_year + AAI + election_year, data = ama_model_lag,
                         model = "within", index = "president")
d2 <- plm(EI_vs_all ~ as.factor(location_cat) +
                         def_year + AAI + election_year, data = ama_model_lag,
                         model = "within", index = "president")
d3 <- plm(SD_vs_all ~ as.factor(location_cat) +
                         def_year + AAI + election_year, data = ama_model_lag,
                         model = "within", index = "president")
d4 <- plm(sov_vs_all ~ as.factor(location_cat) +
                         def_year + AAI + election_year, data = ama_model_lag,
                         model = "within", index = "president")
d5 <- plm(amazon_speech ~ as.factor(location_cat) +
                         def_year + AAI + election_year, data = ama_model2_lag,
                         model = "within", index = "president")

stargazer::stargazer(d1, d2, d3,
                     d4, d5, digits = 6,
                     no.space = TRUE,
                     title = "Logistic Regressions with president fixed-effects")

>>>>

amazon_def_year$year <- amazon_def_year$year + 1
adr <- data.frame(year = c(1985, 1986, 1987, 1988),
def_year = c(21.050, 21.050, 21.050, 21.050))
amazon_def_year <- rbind(adr, amazon_def_year) # Missing year data 

@@

         peak_year = ifelse(grepl("1989|1992|2009|2015|2019", year), 1, 0),

@@

ama_model2_lag <- dplyr::select(pop, -text) %>%
  dplyr::left_join(amazon_def_year, by = "year") %>%
  dplyr::left_join(AAI, by = "year") %>%
  filter(location_cat != "Non Identified") %>%
  dplyr::mutate(location_cat = ifelse(grepl("parana|paraiba|mato grosso|mato grosso do sul", location, ignore.case = TRUE), "Non Amazonian States", location_cat),
         location_cat = ifelse(grepl("paraguay", location, ignore.case = TRUE),
                               "International", location_cat),
         location_cat = factor(ifelse(grepl("Bolivia|Peru|Ecuador|Colombia|Venezuela|Guyana|Suriname",
                                            location), "Amazonian Countries",
                                      location_cat),
                               levels = c("Amazonian States",
                                          "Amazonian Countries",
                                          "International", "Brasilia",
                                          "Non Amazonian States")),
         election_year = ifelse(grepl("1989|1994|1998|2002|2006|2010|2014|2018",
                                      year), 1, 0),
         peak_year = ifelse(grepl("1989|1992|2009|2015|2019", year), 1, 0))

#table(ama_model$president, ama_model$party)
#ideology_vdem <- readRDS("~/Documents/GitHub/amazondef/Submission/V-Dem-CPD-Party-V2.rds") %>% 
#dplyr::filter(country_name == "Brazil") %>%
#dplyr::select(v2pashname, v2xpa_antiplural, v2xpa_popul, v2pariglef) %>%
#tidyr::drop_na() %>%
#dplyr::rename(party = v2pashname) %>%
#group_by(party) %>%
#summarise(anti_pluralism = mean(v2xpa_antiplural),
#populism = mean(v2xpa_popul),
#left_right = mean(v2pariglef))
#ama_model_lag <- dplyr::left_join(ama_model_lag, ideology_vdem)
#ama_model2_lag <- dplyr::left_join(ama_model2_lag, ideology_vdem)

@@

```{r models, fig.cap="Logistic Regressions without controls", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE, results="asis"}

# model
a1 <- glm(con_vs_all ~ as.factor(location_cat),
family=binomial(link = "logit"),
                       data = ama_model_lag)
a2 <- glm(EI_vs_all ~ as.factor(location_cat),
family=binomial(link = "logit"),
                      data = ama_model_lag)
a3 <- glm(SD_vs_all ~ as.factor(location_cat),
                      family=binomial(link = "logit"), data = ama_model_lag)
a4 <- glm(sov_vs_all ~ as.factor(location_cat),
                       family=binomial(link = "logit"), data = ama_model_lag)

stargazer::stargazer(a1, a2, a3, a4, digits = 6, no.space = TRUE,
                     title = "Logistic regressions without controls")

@@

```{r models lagged, fig.cap="Logistic Regressions with controls", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE, results="asis"}

# model 2
b1 <- glm(con_vs_all ~ as.factor(location_cat) + def_year + AAI +
election_year + peak_year,
family=binomial(link = "logit"),
                       data = ama_model_lag)
b2 <- glm(EI_vs_all ~ as.factor(location_cat) + def_year + AAI +
election_year + peak_year,
family=binomial(link = "logit"),
                      data = ama_model_lag)
b3 <- glm(SD_vs_all ~ as.factor(location_cat) + def_year + AAI +
election_year + peak_year,
                      family=binomial(link = "logit"), data = ama_model_lag)
b4 <- glm(sov_vs_all ~ as.factor(location_cat) + def_year + AAI +
election_year + peak_year,
                       family=binomial(link = "logit"), data = ama_model_lag)

stargazer::stargazer(b1, b2, b3, b4, digits = 6, no.space = TRUE,
                     title = "Logistic regressions with controls")

@@

```{r models president fixed effect, fig.cap="Fixed-effects logistic regressions by presidents with controls", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE, results="asis"}

# model 3
c1 <- plm(con_vs_all ~ as.factor(location_cat) + 
                         def_year + AAI + election_year + peak_year,
                         data = ama_model_lag,
                         model = "within", index = "president")
c2 <- plm(EI_vs_all ~ as.factor(location_cat) +
                         def_year + AAI + election_year + peak_year,
                         data = ama_model_lag,
                         model = "within", index = "president")
c3 <- plm(SD_vs_all ~ as.factor(location_cat) +
                         def_year + AAI + election_year + peak_year,
                         data = ama_model_lag,
                         model = "within", index = "president")
c4 <- plm(sov_vs_all ~ as.factor(location_cat) +
                         def_year + AAI + election_year + peak_year,
                         data = ama_model_lag,
                         model = "within", index = "president")

stargazer::stargazer(c1, c2, c3, c4, digits = 3, no.space = TRUE,
                     title = "Fixed-effects logistic regressions by president with controls",
                      column.sep.width = ".001pt",
                      font.size="small")
```

@@
